Suboptimality Bounds for Approximate State Abstraction

### 2016-02-02 paper/theory_results.tex
Reorganize tex so less conflicts

\documentclass{article}
\usepackage{times}
\usepackage{graphicx}
\usepackage{subfigure} 
\usepackage{natbib}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{amsthm}%For stating numbered theorems
\usepackage{amsfonts}
\usepackage{algorithmic}
\usepackage{subfigure}
\usepackage{hyperref}
\newcommand{\theHalgorithm}{\arabic{algorithm}} % Fixes misbehavior of conflicting packages.
\usepackage{icml2016/icml2016} 
\usepackage[nolist]{acronym} % Acronym package -- give argument <dua> to suppress acronym usage

%THeorem declarations
\newtheorem{thm}{Theorem}
\newtheorem{lma}{Lemma}
\newtheorem{clm}{Claim}
\newtheorem{defn}{Definition}

\icmltitlerunning{Suboptimality Bounds for Approximate State Abstraction}

% --- Notation Commands ---
\newcommand{\ep}{\widetilde \phi}
\newcommand{\epQ}{\ep_{Q^*}}
\newcommand{\epM}{\ep_{\text{model}}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\mcS}{\mathcal{S}}
\newcommand{\mcT}{\mathcal{T}}
\newcommand{\mcR}{\mathcal{R}}
\newcommand{\pM}{\phi_{\text{model}}}

% --- Note Commands ---
\usepackage{color}
\newcommand\dnote[1]{\textcolor{blue}{Dave: #1}}
\newcommand\enote[1]{\textcolor{green}{Ellis: #1}}

% --- DOCUMENT ---
\begin{document}

\twocolumn[
\icmltitle{Suboptimality Bounds for Approximate State Abstraction}

% Paper Meta Info
\icmlauthor{David Abel}{david_abel@brown.edu}
\icmladdress{Brown University,
            115 Waterman Street, Providence, RI 02906}
\icmlauthor{D. Ellis Hershkowitz}{david_hershkowitz@brown.edu}
\icmladdress{Brown University,
            115 Waterman Street, Providence, RI 02906}
\icmlauthor{Michael L.\ Littman}{michael_littman@brown.edu}
\icmladdress{Brown University,
            115 Waterman Street, Providence, RI 02906}

\icmlkeywords{Reinforcement Learning, State Aggregation, State Abstraction, Planning, MDP}

\vskip 0.3in
]

%Acronyms -- use \ac for acronym or \acp for plural/capitalization of acronym
\begin{acronym}
\acro{MDP}{Markov Decision Process}
\acrodefplural{MDP}[MDPs]{Markov Decision Processes}
\acro{RL}{reinforcement learning}
\acrodefplural{RL}{Reinforcement learning}
\end{acronym}

% --- ABSTRACT ---
\begin{abstract}
The combinatorial explosion that plagues planning and \ac{RL} algorithms can be moderated using abstraction. For instance, prohibitively difficult task representations can be condensed, preserving essential information such that solutions are tractably computable. In this work, we investigate a theoretical framework for approximate state abstraction that achieves high degrees of compression while preserving near optimal behavior. \ac{RL} agents using these abstractions treat experiences that resemble each other as equivalent, and generalize knowledge to novel scenarios based on prior experiences. We present theoretical guarantees of the quality of value functions derived from four classes of approximate state abstraction. Additionally, we empirically evaluate the relationship between the degree of approximation and the degree of abstraction achieved in a variety of example tasks, as well as the tradeoff between the degree of approximation and the optimality of behavior.
\end{abstract}

% --- SECTION: Introduction ---
\section{Introduction}
Abstraction plays a fundamental role in learning. Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems. However, in natural environments, no two states are identical. This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.

% Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{papadimitriou1987complexity,littman1995complexity}. Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}. Although polynomial runtime or sample complexity may seem like a reasonable constraint, due to Bellman's curse of dimensionality, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain. Thus, bounds polynomial in state space size often translate to intractable problems for sufficiently complicated tasks. \dnote{Would prefer a different example} For instance, a robot involved in a pick and place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider to do so grows exponentially with the number of objects it plans over \enote{Cite Dabe Icaps}.

% Existing work on state abstraction.
Thus, a key research agenda for planning and RL is leveraging abstraction to reduce large state spaces~\cite{andre2002state,jong2005state,dietterich2000hierarchical,Bean2011}. These methods are characterized by reducing \textit{ground} MDPs with large state spaces to \textit{abstract} MDPs with smaller state spaces by aggregating states according to some notion of equality or similarity. Existing work has characterized how aggregation of states with equal values of particular quantities fully maintains optimality~\cite{li2006towards,dean1997modelmin}. However, exactly solving for these quantities is itself computationally taxing and often as difficult as solving for optimal behavior in the ground \ac{MDP}, thereby defeating the purpose of abstraction.

% Approximate abstraction
In this work, we demonstrate that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy. Relaxing the aggregation criteria from equality of quantities to $\varepsilon$-closeness offers two benefits. First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge that we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}. Second, because the state-aggregation criteria are relaxed to approximate equality, methods that employ approximate equality are able to tune the aggressiveness of state aggregation all the while incurring bounded error.

% Summary	
This paper is organized as follows. We first introduce the necessary terminology and background of \ac{RL} and state abstraction. We then survey existing types in state abstraction as applied to sequential decision making. The following section introduces our four primary results; bounds on the error guaranteed by four classes of approximate state abstraction. We then discuss experiments in which we apply one class of approximate abstraction to a variety of different tasks, visualizing the abstractions and showing the relationship between degree of compression and error incurred.

% --- SECTION: Background ---
\section{Background}

First, some background.

%MDP/SDM Background and Notation
\subsection{\acp{MDP} and Sequential Decision Making}
An \ac{MDP} is a five-tuple: $\langle \mathcal{S}, \mathcal{A}, \mathcal{T}, \mathcal{R}, \gamma \rangle$: $\mathcal{S}$ is a finite state space; $\mathcal{A}$ is the set of actions available to the agent; $\mathcal{T}$ denotes $\mathcal{T}(s' \mid s,a)$, the probability of an agent applying action $a \in \mathcal{A}$ in state $s \in \mathcal{S}$ resulting in arriving in $s' \in \mathcal{S}$; $\mathcal{R}(s)$ denotes the reward received by the agent arriving in state $s$; $\gamma \in [0, 1]$ is a discount  factor that defines how much the agent prefers future rewards over immediate rewards. We assume without loss of generality that all reward functions are normalized to $[0,1]$.

The goal of an agent in an \ac{MDP} is to solve for a policy that maps states to actions: $\pi: \mathcal{S} \rightarrow \mathcal{A}$. In particular, the agent wants to solve for the policy that maximizes its expected discounted reward from any state. This goal policy is denoted $\pi^*$. We denote the expected discounted reward for following policy $\pi$ from state $s$ as the value of the state under that policy, $V^\pi(s)$. We similarly denote the expected discounted reward for taking action $a \in \mathcal{A}$ and then following policy $\pi$ from state $s$ forever after as $Q^\pi(s,a)$. Lastly, we denote the value and $Q$ functions under the optimal policy as $V^*$ and $Q^*$, respectively. \enote{Add citation -- either Littman review paper or Sutton/Barto or Puterman}

\enote{Define value of state under a policy}

%Lihong Section
\subsection{Abstraction Notation}
We build upon the notation used by \citeauthor{li2006towards} \enote{This should probably say more}.

We understand an abstraction as a mapping from the state space of a ground MDP $M_G$ to that of an abstract MDP $M_A$ using a state-aggregation scheme. $M_G = \langle \mathcal{S}_G, \mathcal{A}, \mathcal{T}_G, \mathcal{R}_G, \gamma \rangle$ and $M_A = \langle \mathcal{S}_A, \mathcal{A}, \mathcal{T}_A, \mathcal{R}_A, \gamma \rangle$.

% States
The states in the abstract \ac{MDP} are constructed by applying a state-aggregation function, $\phi$, to the states in the ground \ac{MDP}, $\mathcal{S}_A$. More specifically, $\phi$ maps a state in the ground \ac{MDP} to a state in the abstract \ac{MDP}:
\begin{equation}
\mathcal{S}_A = \{ \phi(s) \mid s \in \mathcal{S}_G\}.
\end{equation}

Intuitively, the abstract reward function and abstract transition dynamics for each abstract state are a weighted combination of the rewards and transitions for each ground state in the partition. We make no assumptions about the weighting scheme, except that the weighting is a convex combination across all states in the partition.

% Reward
The abstract reward function $\mathcal{R}_A(s,a)$ is a weighted sum of the rewards of each of the ground states that map to the same abstract state:
\begin{equation}
\mathcal{R}_A(s,a) = \sum_{g \in \phi(s), s \in \mathcal{S}_G} \mathcal{R}_G(g,a) \omega(g) .
\end{equation}
% zzz g in phi(s) seems like a type error, no?

% Transition
The abstract transition function $\mathcal{T}_A(s,a,s')$ is a weighted sum of the transitions of each of the ground states that map to the same abstract state:
\begin{equation}
\mathcal{T}_A(s,a,s') = \sum_{g \in \phi^{-1}(s)} \sum_{g' \in \phi^{-1}(s')} \mathcal{T}_G(g,a,g') \omega(g),
\end{equation}
\noindent where $
s, s' \in \mathcal{S}_A
$.

% Abstract policy in ground.
In general, we are interested in how policies defined over the abstract \ac{MDP} perform in the ground \ac{MDP}. To evaluate a policy $\pi_A:\mathcal{A}\rightarrow\mathcal{A}$, we map a ground state into the abstract state space, and query the abstract policy for behavior. Specifically:
\begin{equation}
V^{\pi_A}(s) = \mathcal{R}_G(s,\pi_A(\phi(s))) + \gamma \sum_{s' \in \mathcal{S}_G} \mathcal{T}_G(s,\pi_A(\phi(s)),s')V^{\pi_A}(s').
\end{equation}

\enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}
\enote{Say more about the weighting, w(s), (that it sums to 1 but that's all we assume)}

% Subsection: Exact Abstraction Framework
\subsection{Exact Abstraction Framework}

\citeauthor*{li2006towards} developed a framework for state abstraction in \acp{MDP}, the notation for which is defined in the previous section. Here, we survey their main results, which we then extend to the framework of approximate abstraction.

In particular, the authors define the following five classes of state-aggregation functions, inspired by existing methods for state abstraction in \acp{MDP}. For brevity, we include those that we build upon directly. (See their paper for full details.)

\begin{defn}
A $Q^*$-irrelevance abstraction, $\phi_{Q^*}$, is one such that:
\begin{equation}
\phi_{Q^*}(s_1) = \phi_{Q^*}(s_2) \rightarrow \forall a\ \left(Q^*(s_1,a) = Q^*(s_2,a)\right).
\end{equation}
\end{defn}

\begin{defn}
A model-irrelevance abstraction, $\phi_{model}$, is one such that:
\begin{multline}
\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \forall a\ \mathcal{R}_G(s_1,a) = \mathcal{R}_G(s_2,a). \\
\end{multline}
and
\begin{multline}
\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \\ \forall a \sum_{s' \in \phi^{-1}(\phi(s_1))} \mathcal{T}_G(s_1,a,s') =\sum_{s' \in \phi^{-1}(\phi(s_2))} \mathcal{T}_G(s_2,a,s'). \\
\end{multline}
\end{defn}

In words, zzz.

% --- SECTION: Related Work ---
\section{Related Work}

Several other projects have addressed similar topics.

% Approximate abstraction work.
%Dean: 
%\begin{itemize}
%\item \citep{dean1997model} Does abstraction with model equality.
%\item \citep{dean1997modelmin} Does approximate abstraction with model similarity.
%\end{itemize}
%
%Boutilier:
%\begin{itemize}
%\item ~\citep{dearden1997abstraction} Abstraction: a similar ish bound with a similar is agenda.
%\item ~\citep{Boutilier2000} Stochastic DP: tree based policies, sort of bound thingies.
%\end{itemize}
%
%Even~\cite{even2003approximate}: COLT paper on different metrics
%
%Ortner:
%\begin{itemize}
%\item ~\cite{ortner2013adaptive}: Uses Dean results to do UCRL online learning of abstraction. 
%\item ~\cite{odalric2013optimal}: Learn which abstraction to use online (similar to the Nan paper)
%\end{itemize}

\subsection{Approximate State Abstraction}
\citeauthor*{dean1997model} investigated partitioning an MDP's state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other. They provide bounds on the error incurred as a result of using the optimal policy defined over these blocks in the original MDP. This method of abstraction is effectively characterized as a function belonging to the approximate class $\phi_{model}$.
Several approaches build on the notion of $\epsilon$-homogeneity. \citeauthor*{even2003approximate} analyzed different distance metrics used in the process of identifying $\epsilon$-homogenous partitions. \citeauthor*{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $T$ and $R$ provided by UCRL~\cite{auer2009near}.

%Prior work considers abstractions related to transition model similarity, or both transition model and reward function similarity with the aim of reducing the state space size required for planning and learning while still achieving a bounded error solution~\cite{even2003approximate,ortner2013adaptive,Boutilier2000}. All of this work is closely in line with our own agenda; they investigate rules for abstractions that may inform a reduced, abstract MDP, the solution to which has bounded error in the original MDP. However, all prior results explore model similarity abstraction rules, whereas we consider several broader classes of approximate abstraction. Furthermore, our results depend on no assumptions regarding the structure of the MDPs in which we apply our abstraction, and generalize to both the reinforcement learning or the planning setting, while many previous approaches require simplifying assumptions about the space of MDPs\dnote{a comment about what assumptions are made would be nice}, or only work target planning.

\subsection{Specific Abstraction Algorithms}
Many previous works have targeted the creation of algorithms that enable state abstraction for MDPs. \citeauthor*{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction. Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstractions that maintain optimality. \citeauthor{dietterich2000hierarchical} developed the MAXQ algorithm, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied. \citeauthor*{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away ignored in a factored-state \ac{MDP}. The agent will learn to ignore state variables that don't impact optimal behavior, making this method a version of the approximate $\phi_{a^*}$ work. For a full survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citeauthor{li2006towards}.

% Other? Selecting abstractions
%\subsection{Selecting Abstractions}
%\citep{jiang2015abstraction} investigate the question of choosing between two abstractions during learning. They provide analysis for an online approach to identifying the better abstraction.

% Defining

% Critically, our work differs from these in that our primary aim is to achieve understanding of what methods of abstraction in reinforcement learning can maintain bounded error solutions, while these focus on particular strategies that fit within our framework.

% Lihong/Walsh/Littman: Towards a unified theory...

%\begin{itemize}
%\item {\bf Approximate equivalence of MDP}~\cite{even2003approximate}
%\item ALisp~\cite{andre2002state}
%\item Aggregation in DP~\cite{Bean2011}
%\item {\bf Does approximate aggregation and then UCRL}~\cite{ortner2013adaptive}
%Very similar to our overall goal: learn an abstraction function online using confidence bounds as the epsilon. Wowza. Only uses the whole model similarity business though. Seems to be the case for all of the approximate aggregation work (just does the bisimulation or $\epsilon-homogeneity$)
%
%\item Selecting the state rep in RL~\cite{maillard2011selecting}
%\item Near optimal state reps~\cite{ortner2014selecting}
%\item SMDP homomorphisms~\cite{ravindran2003smdp}
%\end{itemize}

@@

% zzz that's odd... sounds like the same thing twice but with optimal policy added. we'll see how that works.

@@

It follows that the Q-value of a state $s$ in $M^T$ for action $a$ is defined by:
% zzz too long... needs to be broken up.
% zzz also, I'm not sure we want the temporally heterogeneous MDP to change state spaces mid stream. I think it should all be in terms of the ground MDP (but with the phi function used as needed)
% zzz also, ``w(g)'' comes out of the blue... there's got to be a better notation here.
\begin{equation}
Q_T(s, a) = 
\begin{cases}
	   Q_G(s, a) &  T=0\\
	   \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right] & T = 1\\
	   \mathcal{R}_A(\epQ(s),a) + \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a') & \text{o/w}
\end{cases}
\end{equation}

@@

% -----------------------------------------------
% --- SECTION: Example Domains ---
% -----------------------------------------------
\section{Example Domains}

\enote{Note somewhere why we selected these MDPs -- b/c a wide variety}

To demonstrate the efficacy of these approximate abstraction functions, we test functions in the $\ep{Q^*}$ abstraction family on a variety of domains. We compare the number of states in the abstract MDP to different values of $\epsilon$, as well as the value difference between the optimal policy in the abstract MDP compared to the ground MDP. More specifically, we relate $\epsilon$ to:
\begin{equation}
|V^{\pi_G^*}(s_{init}) - V^{\pi_A^*}(s_{init})|
\end{equation}
For different values of $\epsilon$.

% Description of visuals.
Our code base provides implementations to visualize, abstract, and evaluate arbitrary MDPs to promote further investigation into approximate abstraction. The included visuals of compressed MDPs always converts MDPs into a graph so that an arbitrary MDP may be visualized when abstracted. We use the graph visualization library GraphStream~\cite{graphstream}. In our visuals, a grey circle indicates a state, while the colored arrows indicate transitions. The thickness of the arrow indicates how much reward is associated with that transition. In the ground MDPs, states are labeled with a number. In some abstract MDPs, we indicate which ground states were collapsed to each abstract state (some are visually unwieldy and so were ignored).

\dnote{One thing we want to add is a description of how diverse these domains are!}
\dnote{Also put in a note that we're using a uniform weighting scheme}

% Subsection: NChain.
\subsection{NChain}

NChain is a simple MDP heavily investigated in the Bayesian Reinforcement Learning literature due to the interesting exploration problem it poses. \dnote{More description of Nchain}

% NChain Compression Visuals.
\begin{figure}[h]
\subfigure[Ground NChain]{
\includegraphics[width=0.48\columnwidth]{figures/ground_nchain.png}}
\subfigure[Abstract NChain]{
\includegraphics[width=0.48\columnwidth]{figures/abs_nchain.png}}
\label{fig:nchain-visual}
\caption{Comparison of Original NChain MDP and Abstract NChain MDP, under an $\epQ$ abstraction, with $\epsilon=0.5$}
\end{figure}

%% Subsection: UpWorld.
%\subsection{UpWorld}
%
%The UpWorld task is an $N\times M$ grid in which the agent starts in the lower left corner. The agent may move left, right, and up. The agent receives positive reward for transitioning to a state at the top of the grid, where moving up in the top cells self transitions. the agent receives 0 reward for all other transitions. Consequently, moving up is always the optimal action, since moving left and right does not change the agent's manhattan distance to positive reward. During experimentation, we set $N=10$, $M=4$.
%
%\begin{figure}
%\subfigure[Ground UpWorld]{
%\includegraphics[width=0.48\columnwidth]{figures/ground_upworld.png}}
%\subfigure[Abstract UpWorld]{
%\includegraphics[width=0.48\columnwidth]{figures/abs_upworld.png}}
%\label{fig:upworld-visual}
%\caption{Comparison of Original UpWorld MDP and Abstract MDP, under $\epQ$, with $\epsilon=0.5$}
%\end{figure}

% Subsection: Taxi
\subsection{Taxi}

Taxi has long been studied by the hierarchical reinforcement learning literature due to its natural decomposition into subgoals. The agent may move left, right, up, and down, as well as pickup a passenger and drop off a passenger. The agent must seek out passengers and take them to their destination. We visualize the compression on a simple 626 Taxi instance in Figure~\ref{fig:taxi-visual}. As stated above, we visualize the original Taxi problem into a graph representation so that we may visualize both the ground MDP and compressed MDP in the same format.

% Taxi Compression Visuals
\begin{figure}[h]
\subfigure[Ground Taxi]{
\includegraphics[width=0.48\columnwidth]{figures/ground_taxi.png}}
\subfigure[Abstract Taxi]{
\includegraphics[width=0.48\columnwidth]{figures/abs_taxi.png}}
\label{fig:taxi-visual}
\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under an $\epQ$ abstraction, with $\epsilon=0.03$}
\end{figure}

% Insert visual and/or stats on number of states and performance of VI solving the abstract MDP and evaluating the resulting policy on the original MDP

% Subsection: Minefield.
\subsection{Minefield}

Minefield is a slight variant of Grid World. The transitions and rewards are perturbed slightly, and there is no down action. In particular, there is some slip probability associated with movement; when the agent moves left or right, it has probability $x$ of moving up, when the agent moves up, it has probability $\frac{x}{2}$ of moving left, and probability $\frac{x}{2}$ of moving right. The reward function is such that transitions to the top row in the grid receive $1.0$ reward, all other transitions receive $0.2$ reward, except for a random set of $\kappa$ states (which may include the top row) that receive $0$ reward (these are the states with mines in them, thus the name). During experimentation, we set $N=10, M=4, \epsilon=1.1, \kappa = 5, x = 0.01$.

% Minefield Compression Visuals
\begin{figure}
\subfigure[Ground Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/ground_minefield.png}}
\subfigure[Abstract Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
\label{fig:minefield-visual}
\caption{Comparison of Original Minefield MDP and Abstract MDP, under an $\epQ$ abstraction, with $\epsilon=1.1$}
\end{figure}

% Subsection: Random.
\subsection{Random}

The Random MDP domain we consider is as follows. There are $N$ states, and $K$ actions. For each state, each action can transition to two randomly selected (but fixed) states, each with probability $0.5$.

% Random Compression Visuals
\begin{figure}
\subfigure[Ground Random]{
\includegraphics[width=0.48\columnwidth]{figures/ground_random.png}}
\subfigure[Abstract Random]{
\includegraphics[width=0.48\columnwidth]{figures/abs_random.png}}
\label{fig:minefield-visual}
\caption{Comparison of Original Random MDP and Abstract Random MDP, under an $\epQ$ abstraction, with $\epsilon=0.2$}
\end{figure}

% --- SECTION: Approximate Abstraction on Example Domains ---
\section{Approximate Abstraction on Example Domains}

Here we discuss the results shown in states blah blah \dnote{Description of this section}.

\begin{itemize}
\item For $\epsilon > 0$, there are extremely useful abstractions to be made. Want to emphasize that with approximate knowledge of X, can still abstract effectively (point out Minefield + NChain both retain a very good policy from abstract MDP). This hits the learnable point.
\item Explain goal based/Taxi (regenerate plot for different scale of epsilon)
\item Possibly talk about stochasticity (low priority)
\item Explain Random behavior, smooth interpolation, mention randomness, etc.
\item Describe plots a bit (what is the y-axis?)
\end{itemize}

% Figure: Epsilon vs. #States for all three sample domains.
\begin{figure}
\centering
\subfigure[NChain]{
\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.png}}
\subfigure[Taxi]{
\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.png}}
\subfigure[Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.png}}
\subfigure[Random]{
\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_num_abstract_states.png}}
\label{fig:eps-states}
\caption{$\epsilon$ vs. Num States}
\end{figure}

% Figure: Epsilon vs. Error in Abstract Value Function
\begin{figure}
\subfigure[NChain]{
\includegraphics[width=0.48\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
\subfigure[Taxi]{
\includegraphics[width=0.48\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.png}}
\subfigure[Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy_init_ground_state}}
\subfigure[Random]{
\includegraphics[width=0.48\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy_init_ground_state}}
\label{fig:eps-states}
\caption{$\epsilon$ vs. the Value under the Abstract Policy in the Initial Ground State}
\end{figure}

% --- SECTION: Conclusion ---
\section{Conclusion}

% Summary

% Future Work
\begin{enumerate}
\item Learning Phi
\begin{itemize}
\item Exploration vs. Exploitation problem is different while trying to learn Phi
\end{itemize}
\item Compressibility
\begin{itemize}
\item Relationship between approximate abstract and compressibility
\end{itemize}
\item POMDP and abstraction
\end{enumerate}

% --- BIBLIOGRAPHY ---
\bibliographystyle{icml2016/icml2016}
\bibliography{state_abs}

\end{document}

>>>>

@@

% zzz that's odd... sounds like the same thing twice but with optimal policy added. we'll see how that works.
% In response^^^ Could add a sentence pointing out how these differ.

@@

It follows that the Q-value of a state $s$ in $M^T$ for action $a$ is defined by:
% zzz too long... needs to be broken up.
% zzz also, I'm not sure we want the temporally heterogeneous MDP to change state spaces mid stream. I think it should all be in terms of the ground MDP (but with the phi function used as needed)
% zzz also, ``w(g)'' comes out of the blue... there's got to be a better notation here.
\dnote{Let's put a reminder of the weighting scheme here}
\begin{equation}
Q_T(s, a) = 
\begin{cases}
	   Q_G(s, a) &  T=0\\
	   \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right] & T = 1\\
	   \mathcal{R}_A(\epQ(s),a) + \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a') & \text{o/w}
\end{cases}
\end{equation}

@@
